Layered Types -- A structured approach to arbitrarily combine Type Systems

### 2023-01-30 paper/implementation.tex
* Added outline description for use case 2

To demonstrate our layered approach we implemented a simple functional language. The syntax of said language is described in \ref{fig:lang}. The language is similar to most simple functional languages and generally follows the reduction semantics of a standard Hindley-Milner type system. The only data types available in the language are the \texttt{Int} and the \texttt{Bool} type. However, the language does not strictly require the programmer to explicitly specify the type of a variable.

@@

These layers can then be used to define properties. Depending on the Layers' implementation, these properties can apply to identifiers or can be used to define properties of the type system the layer defines. In a very basic and minimal approach these layers can be used to annotate types to variables and functions. Additionally, one might add additional layers to a variable to ensure more properties. Each layer will be checked individually and independently. A more detailled approach of the architecture behind our layered approach will be described in section \ref{ssec:architecture}.

>>>>

To demonstrate our layered approach we implemented a simple functional language. The syntax of said language is described in Fig. \ref{fig:lang}. The language is similar to most simple functional languages. Implicitly, our language natively supports \textt{Boolean} and \texttt{Integer} datatypes through the available constants. However, the language on it's own does not require any type annotations.

@@

These layers can be used to define properties. Depending on the specific implementation of a layer, these properties can apply to identifiers or can be used to define properties of the type system the layer defines. In a very basic and minimal approach these layers can be used to annotate types to variables and functions. Additionally, one might add additional layers to a variable to ensure more properties. Each layer will be checked individually and independently. A more detailled approach of the architecture behind our layered approach will be described in section \ref{ssec:architecture}.
